---
title: "Da Project"
author: "Chard"
date: '2022-06-29'
output: pdf_document
---

First step is installing necessary packages 
```{r}
install.packages("haven")
library("haven")
library("dplyr")
```

Then, next step is to read Sas files using read_sas() function, and putting them into variables
```{r}
screen_18 = read_sas("/Users/richardlim/Desktop/Cosibs/project/nsch_2018_screener_SAS/nsch_2018_screener.sas7bdat"); screen_18
top_18 = read_sas("/Users/richardlim/Desktop/Cosibs/project/nsch_2018_topical_SAS/nsch_2018_topical.sas7bdat"); top_18
screen_19 = read_sas("/Users/richardlim/Desktop/Cosibs/project/nsch_2019_screener_SAS/nsch_2019_screener.sas7bdat"); screen_19
top_19 = read_sas("/Users/richardlim/Desktop/Cosibs/project/nsch_2019_topical_SAS/nsch_2019_topical.sas7bdat"); top_19
```

Once the files are read into R, the next step is to combine the 2018 and 2019 data sets respectively 
```{r}
merged_18 = merge(screen_18, top_18, by.x = "HHIDS", by.y = "HHID", all.x = T, all.y = T); merged_18
merged_19 = merge(screen_19, top_19, by.x = "HHIDS", by.y = "HHID", all.x = T, all.y = T); merged_19
```

Getting the variables we want and turning them into a new variable
```{r}
cleanv18 = merged_18 %>% select(HHIDS, C_AGE_YEARS, C_HISPANIC_R, C_RACE_R, C_SEX, BMICLASS, OVERWEIGHT, PHYSACTIV, SCREENTIME, HOURSLEEP, K2Q32A, K2Q32B, K2Q32C, K2Q33A, K2Q33B, K2Q33C, HEART_CURR); cleanv18
cleanv19 = merged_19 %>% select(HHIDS, C_AGE_YEARS, C_HISPANIC_R, C_RACE_R, C_SEX, BMICLASS, OVERWEIGHT, PHYSACTIV, SCREENTIME, HOURSLEEP, K2Q32A, K2Q32B, K2Q32C, K2Q33A, K2Q33B, K2Q33C, HEART_CURR); cleanv19
```

Merging clean variable data sets
```{r}
cleanvt = merge(cleanv18, cleanv19, all.x = T, all.y = T); cleanvt
```

Filtering the data set to only include 13-18 year old
```{r}
agef = filter(cleanvt, C_AGE_YEARS > 12 & C_AGE_YEARS < 19 & HEART_CURR == '1'); agef
```
